\Title

### 2021-01-14 manuscript/manuscript.tex
Reorganize results into a "Synthetic data" section
This will group all results from synthetic data applications. Moved the
discussion subsection to a "Discussion" section where we'll discuss all
of the results from the paper.
Start including Australia gravity into manuscript

>>>>

Our final goal is to show how gradient-boosted equivalent sources can be used
to interpolate a very large dataset of gravity data into a regular grid.
We selected a compilation of gravity surveys over Australia made by
\citet{wynne2018}.
It consists in more than 1.7 million data points that cover most part of the
Australia territory obtained through observations on ground
(see Fig.~\ref{fig:australia-data}).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/australia-data.pdf}
    \caption{
    }
    \label{fig:australia-data}
\end{figure}

First we compute the gravity disturbance by removing the normal gravity from
the observed gravity data (see Fig.~\ref{fig:australia-disturbance}).
The normal gravity is computed on each observation point through the
closed-form formula given by \citet{li2001} and using the WGS84 ellipsoid as
reference.
Then we obtain plain coordinates of the observation points by applying
a Mercator projection.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/australia-disturbance.pdf}
    \caption{
    }
    \label{fig:australia-disturbance}
\end{figure}

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaRelativeDepth{}.
The choice of the block spacing must be done taking into account the desired
resolution of the final grid.
If the grid will have a much higher resolution than the block spacing, the
equivalent sources will not be able to reproduce the high frequency components
of the data.
Therefore we recommend setting a block spacing that matches the resolution of
the final grid.
In this case we will generate a regular grid with a resolution of 1~arc-minute,
which can be approximated by \SI{1.8}{\kilometer} for the Earth.
